ms2

### 2017-08-24 ms2/ms2_display.Rmd
ms2 new plot

>>>>

I contrast this situation against *E. coli* and quinolones. In that case, adding terms to the regression doesn't drastically alter $\beta_{f_>}$.

```{r fnz_mu_ecoliquin}
results %>%
  filter(unit_type=='hrr', model %in% c('univariate_fnz', 'multivariate_fnz_mean', 'multivariate_fnz_mup'), term != '(Intercept)') %>%
  filter(bug=='E. coli', drug_group=='quinolone') %>%
  mutate(model=str_replace(model, '^multivariate_', '')) %>%
  select(bug, drug_group, model, term, estimate) %>%
  spread(term, estimate) %>%
  kable
```
